---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
h2 {
  font-weight: bold;
  padding-left: 200px
}
h4 {
  font-style: italic;
}
p {
  font-weight: lighter
}
body {
  background-color: #808080;
  color: #FFFFFF
}

```

## Exploring the connection between genre, length and views of YouTube videos

This report analyses data collected from six different YouTube video genres: Music, Gaming, Sports, Learning, Fashion & Beauty, and Podcasts. The Movies genre was excluded, as the presentation of data differs greatly from the other genres. The data was collected based on random video selection within each genre, done at a different time of day for each genre to ensure fairness, and recording of the length of the video as well the number of views that it had received.

#### Below is an observation made from summary data, followed by two bar charts.

```{r}

library(tidyverse)

# create data frame
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vT8VMC5JyVaueH4F6-dLnjWbQlaH5OxAObm65CRTTkbxsXgQsr6E3lXDXQe9G-otBYdAYmzYqpLQngK/pub?gid=1566381835&single=true&output=csv")

# create new data frame with renamed variables
latest_data <- logged_data %>%
  rename(video_genre = 2,
         video_length = 3,
         video_views = 4)

# minimum and maximum video lengths
min_length <- min(latest_data$video_length)
max_length <- max(latest_data$video_length)

# group data by genre and find the mean length of videos in each genre
genre_mean_lengths <- latest_data %>%
  group_by(video_genre) %>%
  summarise(mean_length = round(sum(video_length) / length(video_length), 1))

```

The shortest video in this dataset is `r min_length` minutes long, while the longest is `r max_length` minutes long.

The first bar chart compares the average length of videos in each genre. This chart shows that Podcasts have the highest average video length, being around 200 minutes longer than most other genres.

```{r, fig.height = 5, fig.width = 8}

# bar chart of mean video lengths in each genre
ggplot(data = genre_mean_lengths) +
  geom_col(aes(x = video_genre, y = mean_length), fill = "#00bfff") +
  labs(title = "Which Youtube Genre Has the Longest Videos?",
       subtitle = "Comparing genres by the average length of videos in each",
       x = "Video Genre",
       y = "Average Video Length")

```

The second bar chart compares genres by the number of videos in each category of views. It can be inferred that Fashion & Beauty is the highest viewed genre, with 3 out of the 4 randomly selected videos having achieved between 1 and 10 million views.

```{r, fig.height = 5, fig.width = 8}

# bar chart of genre vs view count category
ggplot(data = latest_data) +
  geom_bar(aes(x = video_genre, fill = video_views)) +
  labs(title = "Which YouTube Genre Gets the Highest Views?",
       subtitle = "Comparing genres by the proportion of their videos in view categories",
       x = "Video Genre",
       y = "Number of Videos")

```

